---
title: "FinalExam"
output: html_document
---

 
My research question is: does life expectancy correlate with years of education? I suppose it does. 

I used data that has been wrangled allready.


```{r }
human <- read.csv("http://s3.amazonaws.com/assets.datacamp.com/production/course_2218/datasets/human_development.csv", stringsAsFactors = F)
dim(human)
str(human)
dimnames(human)

```

The data is from the United Nations Development Programme. It contains every coyntry and responds for example to the question: which is each country's life expectancy.

There is more info:
http://hdr.undp.org/en/content/human-development-index-hdi

We can see that data has 8 variables and 195 observations. Dimnames tells the names of variables. 
```{r}
mean(human$Life.Expectancy.at.Birth)
mean(human$Mean.Years.of.Education)
hist(human$Life.Expectancy.at.Birth, col="yellow")
hist(human$Mean.Years.of.Education, col="blue")
```

Mean of life expectancy is about 71 and mean of years of education is about 13. There is allso histograms about those values.

```{r}
fit<- lm(human$Life.Expectancy.at.Birth~human$Mean.Years.of.Education)
summary(fit)

plot(human$Life.Expectancy.at.Birth~human$Mean.Years.of.Education, main="Plot and regression line")
curve(10.515 + 7.432*x, from=0, to=50, add=T, col="deeppink")
```

I wanted to see how mean years of education explains life expectancy. I used simple linear regression analysis. Linear regression analysis concentrates on the relationships of some variables. There is one dependent variable and one or more explanatory variables. In simple linear regression analysis there is only one explanatory. The fitting is done with "least squares approach".

It seems that it really does, because p-value is under 0.001. I draw a plot with deeppink regression line. It seems that higher years of education is related to higher life expectancy.

Now it's really important to notice that correlation is not same as causal connection. We cant't say that there is causal connection between life expectancy and years of education. Let's think about that more. (There might be some causality, because it's possible that when people study they learn somethin important which helps to lengthen their life.) I believe there is third variable that explains the correlation. Usually in countries where are poor and primitive conditions, people dont't educate so long. Healthcare might be bad and so on...

The answer to my question is: yes, life expectancy correlates with years of education.


